\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\ or \\ Charting antigenic drift and evolutionary success of seasonal influenza lineages

### 2013-01-24 flux.tex
Added some of the standard grant numbers.
These are mainly copied from other papers so may need adjustment

TB is supported by the Royal Society. 
MAS is supported by National Institutes of Health grants R01 GM086887 and R01 HG006139 and National Science Foundation grant DMS0856099.
VG, AJH and JWM are funded by MRC reference no U117512723.

>>>>

TB is supported by the Royal Society. 
MAS is supported by National Institutes of Health grants R01 GM086887 and R01 HG006139 and National Science Foundation grant DMS0856099.
The research leading to these results has received funding from the European Research Council under the European Community's Seventh Framework Programme (FP7/2007-2013) under Grant Agreement no. 278433-PREDEMICS and ERC Grant agreement no. 260864.
VG, AJH and JWM are funded by MRC reference no U117512723.
AR acknowledges the support of the Wellcome Trust (grant no. 092807).
Collaboration between MAS, AR and PL was supported by the National Evolutionary Synthesis Center (NESCent), NSF EF-0423641.
DJS and CAR acknowledge EU FP7 programs EMPERIE (223498) and ANTIGONE (278976), Human Frontier Science Program (HFSP) program grant
P0050/2008, Wellcome 087982AIA, and NIH Director's Pioneer Award DP1-OD000490-01.
CAR was supported by a University Research Fellowship from the Royal Society.
